### 2022-08-15 manuscript.Rmd
Initialize TFR topography plot

```{r, tfr, include=TRUE, fig.height=12}
# Read results of cluster-based permutation tests for TFR
read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> tfr_clusters

@@

```{r, eval=FALSE}
# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv")) %>%
  mutate(
    phase = factor(phase, levels = c("Pre-insight", "Insight", "Post-insight")),
    condition = factor(condition, levels = c("Informed", "Naive"))
  ) %>%
  filter(!is.na(condition))

channels <- tfr_grand_ave %>%
  select(-average_by, -phase, -condition, -time, -freq) %>%
  colnames()

tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
tfr_grand_ave_naive <- filter(tfr_grand_ave, condition == "Naive")
tfr_grand_ave_diff <- mutate(tfr_grand_ave_informed, condition = "Difference")
tfr_grand_ave_diff[channels] <- tfr_grand_ave_informed[channels] -
  tfr_grand_ave_naive[channels]

bind_rows(tfr_grand_ave, tfr_grand_ave_diff) %>%
  mutate(
    condition = factor(condition, levels = c("Informed", "Naive", "Difference"))
  ) %>%
  pivot_longer(
    cols = all_of(channels), names_to = "electrode", values_to = "amplitude"
  ) %>%
  select(-average_by, -electrode) %>%
  group_by(phase, condition, time, freq) %>%
  summarise(amplitude = mean(amplitude), .groups = "drop") %>%
  ggplot(aes(x = time, y = freq, fill = amplitude)) +
  facet_grid(phase ~ condition) +
  geom_raster() +
  scale_fill_viridis_c(option = "turbo", limits = c(-0.6, 0.6)) +
  coord_cartesian(expand = FALSE)

tmins <- seq(0.0, 1.2, 0.2)
fmins <- seq(4, 36, 4)

channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))

map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {
  map(tmins, function(tmin, tstep = 0.2) {
    tmax <- tmin + tstep
    map(fmins, function(fmin, fstep = 4) {
      fmax <- fmin + fstep
      tfr_grand_ave_diff %>%
        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
        filter(phase == this_phase) %>%
        pivot_longer(
          cols = all_of(channels), names_to = "electrode", values_to = "power"
        ) %>%
        left_join(channel_locations, by = c("electrode" = "channel")) %>%
        group_by(electrode, x, y) %>%
        summarise(power = mean(power), .groups = "drop") %>%
        eegUtils::topoplot(
          quantity = "power",
          contour = FALSE,
          interp_limit = "skirt",
          scaling = 0.7
        ) +
        scale_fill_viridis_c(limits = c(-0.3, 0.3), option = "turbo") +
        theme(legend.position = "none")
    }) %>%
      plot_grid(plotlist = ., nrow = 1)
  }) %>%
    plot_grid(plotlist = ., nrow = length(tmins))
})
```

>>>>

```{r, tfr, fig.height=12, include=TRUE}
# Read results of cluster-based permutation tests for TFR
read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> tfr_clusters

@@

```{r, fig2, fig.height=10, include=TRUE}
# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv")) %>%
  mutate(
    phase = factor(phase, levels = c("Pre-insight", "Insight", "Post-insight")),
    condition = factor(condition, levels = c("Informed", "Naive"))
  ) %>%
  filter(!is.na(condition))

# Compute difference between conditions within each phase
channels <- channel_locations$channel
tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
tfr_grand_ave_naive <- filter(tfr_grand_ave, condition == "Naive")
tfr_grand_ave_diff <- mutate(tfr_grand_ave_informed, condition = "Difference")
tfr_grand_ave_diff[channels] <- tfr_grand_ave_informed[channels] -
  tfr_grand_ave_naive[channels]

# Plot topography at each time and frequency bin
tstep <- 0.1
fstep <- 4
tmins <- seq(0.0, 0.9, tstep)
fmins <- seq(4, 36, fstep)
map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {
  # map(c("Insight"), function(this_phase) {
  map(tmins, function(tmin) {
    tmax <- tmin + tstep
    map(fmins, function(fmin) {
      fmax <- fmin + fstep
      tfr_clusters %>%
        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
        filter(str_detect(contrast, this_phase) & p_val < .05) %>%
        pull(channel) %>%
        unique() -> significant_channels
      tfr_grand_ave_diff %>%
        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
        filter(phase == this_phase) %>%
        pivot_longer(
          cols = all_of(channels), names_to = "electrode", values_to = "power"
        ) %>%
        left_join(channel_locations, by = c("electrode" = "channel")) %>%
        group_by(electrode, x, y) %>%
        summarise(power = mean(power), .groups = "drop") %>%
        eegUtils::topoplot(
          r = 85,
          quantity = "power",
          contour = FALSE,
          interp_limit = "skirt",
          highlights = significant_channels,
          scaling = 1.1
        ) +
        scale_fill_distiller(limits = c(-0.25, 0.25), palette = "RdBu") +
        # scale_fill_viridis_c(limits = c(-0.25, 0.25)) +
        theme(
          plot.margin = unit(rep(-0.2, 4), "cm"),
          legend.position = "none"
        ) -> topo
      topo$layers[[3]]$aes_params$size <- 0.7
      topo$layers[[4]]$aes_params$size <- 0.7
      topo$layers[[5]]$aes_params$size <- 0.7
      topo$layers[[6]]$aes_params$colour <- NA
      topo$layers[[7]]$aes_params$size <- 0.4
      topo$layers[[7]]$aes_params$colour <- "black"
      topo
    }) -> plotlist
    plotlist <- c(plotlist, list(NULL))
    rel_heights <- c(rep(1, length(fmins)), 0.15)
    if (tmin == min(tmins)) {
      labels <- paste0(fmins, "-", fmins + fstep, " Hz")
      labels <- c(labels, "")
      plot_grid(
        plotlist = plotlist, nrow = length(plotlist),
        rel_heights = rel_heights, labels = labels,
        label_size = 10, label_fontfamily = "Helvetica",
        label_fontface = "plain", label_x = -0.3, label_y = 0.5, vjust = 0.5,
        hjust = 0.5
      )
    } else {
      plot_grid(
        plotlist = plotlist, nrow = length(plotlist), rel_heights = rel_heights
      )
    }
  }) -> plotlist
  tmins_str <- format(tmins, nsmall = 1)
  tmaxs_str <- format(tmins + tstep, nsmall = 1)
  labels <- paste0(tmins_str, "-", tmaxs_str, " s")
  plotlist <- c(list(NULL), plotlist)
  labels <- c("", labels)
  plot_grid(
    plotlist = plotlist, nrow = 1, rel_widths = c(0.6, rep(1, length(tmins))),
    labels = labels, label_size = 10, label_fontfamily = "Helvetica",
    label_fontface = "plain", label_x = 0.5, label_y = 0.01, vjust = 0.5,
    hjust = 0.5
  )
  filename <- paste0("tfr_", this_phase, ".pdf")
  ggsave(filename, width = 12, height = 10)
})
```
